Submission

### 2021-05-10 code/Submission.Rmd
hnng

TODO: add a LATEX cmd for pagebreak here (\ pagebreak) 
## Appdendix

@@

```{r KNOW-Counts, echo=echoval, fig.width=8}
pew %>% ggplot(aes(fill =sumKnowFactor, x = groupKnow)) +
  geom_bar(position = 'dodge', color = 'black') +
  scale_fill_brewer(palette = "Blues") +
  labs(
    title = "Distribution of Tech Literacy Scores",
    y = "Counts",
    x = "Literacy Category",
    fill = "Respondent's\nLiteracy Score",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

@@

#### 4. What situations People Think It Is Acceptable To Use Facial Recognition In the Following Situations?
```{r FACE4_Likert, echo=echoval, message=FALSE}
df_f4 <- pew %>% select(c(FACE4a_W49, FACE4b_W49, FACE4c_W49, FACE4d_W49, groupKnow))

@@

### Additional Tables For Key Figure 1
```{r KF1-tables, echo=echoval}
#Simple simple table of counts
KF1_T1 <- table(pew$sumRTBF, pew$publicDataNum) #public data should be private = 0
colnames(KF1_T1) = c("Data Should Be Private","Data Should Be Public")

>>>>

\pagebreak

## Appdendix

@@

```{r KNOW-Counts, echo=echoval}
pew %>% ggplot(aes(fill =sumKnowFactor, x = groupKnow)) +
  geom_bar(position = 'dodge', color = 'black') +
  scale_fill_brewer(palette = "Blues") +
  labs(
    title = "Distribution of Tech Literacy Scores",
    y = "Counts",
    x = "Literacy Category",
    fill = "Respondent's\nLiteracy Score",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

@@

#### 4. What situations People Think It Is Acceptable To Use Facial Recognition In the Following Situations?

```{r FACE4_Likert, echo=echoval, message=FALSE}
df_f4 <- pew %>% select(c(FACE4a_W49, FACE4b_W49, FACE4c_W49, FACE4d_W49, groupKnow))

@@

### Additional Tables For Key Figure 1

```{r KF1-tables, echo=echoval}
#Simple simple table of counts
KF1_T1 <- table(pew$sumRTBF, pew$publicDataNum) #public data should be private = 0
colnames(KF1_T1) = c("Data Should Be Private","Data Should Be Public")
